% This survey has several scope limitations. First, because agent context compression is evolving rapidly, our synthesis is necessarily representative rather than permanently exhaustive, especially for very recent systems and unpublished engineering practices. Second, we focus on application-level context management during agent execution, and therefore do not attempt a full treatment of neighboring areas such as general long-context modeling, model-level KV-cache optimization, or broader memory architectures except where they directly inform agent compression. Third, our taxonomy prioritizes conceptual unification across targets, mechanisms, policies, failure modes, and evaluation, which improves comparability but cannot fully eliminate heterogeneity in backbone models, task settings, and reporting protocols across the literature. We view these limitations as a consequence of studying a fast-moving systems problem, and hope the framework provided here offers a stable foundation for more exhaustive benchmarked updates as the field matures.

\paragraph{Coverage.} Because agent context compression is evolving rapidly, our synthesis is intended to be representative rather than exhaustive, especially for the newest systems and engineering practices still stabilizing in the literature.

\paragraph{Scope.} We deliberately focus on context compression during agent execution, rather than adjacent areas such as general long-context modeling, context engineering, memory management, or model-level KV-cache optimization, except where they directly inform agent compression. We view these neighboring directions as natural extensions and leave a unified treatment to future work.

\paragraph{Abstraction Level.} Our taxonomy prioritizes conceptual unification across targets, mechanisms, policies, failure modes, and evaluation. This improves comparability, but necessarily abstracts away some implementation-level variation across backbone models, task settings, and reporting protocols.

We view these limitations primarily as boundaries of scope rather than weaknesses of the framework, and hope the structure offered here provides a stable basis for more exhaustive updates as the field matures.



\section*{AI Usage Disclosure}
The authors used AI-based writing assistants to improve grammar, phrasing, and local clarity during manuscript preparation. All AI-assisted suggestions were reviewed, revised, and selectively incorporated by the authors, who take full responsibility for the final text, technical framing, citations, and conclusions.

\section*{Ethical Statement}
This work is a survey of publicly available research papers, technical reports, product documentation, and open-source resources on context management for LLM agents. It does not involve private data, human subjects, or sensitive personal information. We aim to represent prior work accurately and cite sources faithfully; any discussion of deployed systems is based only on publicly accessible evidence and is used solely for scholarly analysis.

